---
title: "Hw-06-ChenchenGuo"
author: "Chenchen GUO"
date: "October 30, 2018"
output: github_document
always_allow_html: yes
---

-   [Introduction](#introduction)

    -[Goals](#goals)
-   [Part1: Character data](#part-1-character-data)

    -[Requirements](#requirements)

    -[Implementation](#implementation)

-   [Part2: File I/O](#part-2-file-io)

    -[Requirements2](#requirements2)

    -[Implementation2](#implementation2)

-   [Part3: Visualization design](#part-3-visualization-design)

    -[Requirements3](#requirements3)

    -[Implementation3](#implementation3)


Introduction
------------

[Homework 06](http://stat545.com/Classroom/assignments/hw06/hw06.html): Data wrangling wrap up

Goals:
------

The first assignment of STAT 547M, complete two of the six topics.

Part 1: Character data
-------------------------

Requirements
------------

Work the exercises in the Strings chapter or R for data science.

Implementation
--------------
Strings charpter

Firstly load all needed packages

```{r}
suppressPackageStartupMessages(library(gapminder))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(stringr))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(broom))
suppressPackageStartupMessages(library(MASS))
```

## 14.2.5 Exercises
### 1. Whats the difference between paste() and paste0()? What the equivalent stringr functions of them? 
```{r}
(name_sports <- paste("Bas", "ket", "ball"))
(name_sports1 <- paste0("Bas", "ket", "ball"))
# The difference between paste() and paste0() is the argument sep by default is " " for paste() and "" for paste0()

# paste0() is equivalent to str_c
(name_sports2 <- str_c("Bas", "ket", "ball"))
# paste() is equivalent to str_c(.., sep = " ")
(name_sports3 <- str_c("Bas", "ket", "ball", sep = " "))

```

### 2. Describe the difference between sep and collapse arguments to str_C()?

```{r}
x <- c("a", "b", "c", "d")
y <- c("w", "x", "y", "z")
paste(x, y, sep="%%")
paste(x, y, collapse="%%")
paste(x, y, sep="%%", collapse=",")
paste(x, y, sep=",", collapse="%%")

# Hence, the sep defines what separates the entries in those tuple-wise concatenations
# the collapse will return any concatenated pairs as part of a sigle length-1 character vector
```

### 3. Use str_lennth() and str_sub() to extract the middle character from a string. What will you do if the string has an even number of length?
```{r}
vec_str <- "asdfghj"
vec_length <- str_length(vec_str)
str_sub(vec_str,(vec_length+1)/2, (vec_length+1)/2)

vec_str1 <- "asdfgh"
vec1_length <- str_length(vec_str1)
str_sub(vec_str1,(vec1_length)/2, (vec1_length)/2+1)
```
### 4. What does str_wrap() do?
```{r}
txt <- c("Jane can run quickly.  So can Dick.",
         "",
         "The quick red fox jumped over the lazy brown dog.")
writeLines(strwrap(txt, width = 25))
writeLines(strwrap(txt, width = 30, indent=5))

# strwrap can print strings into paragraphs
```

### 5. What does str_trim() do?
```{r}
vec_5 <- c("hi", "hello", "Richard Jeffeson")
vec_5
strtrim(vec_5, 7)
```
### 6. Write a function that turns a vector c("a", "b", "c") into the string  a, b, and c.
```{r}
vector_to_string <- function(v){
    if(length(v)==0){
        stop("NA")
    }
    if(length(v)==1){
        return(v)
    }
    str1 <- str_c(v[1:length(v)-1], collapse = ", ")
    str2 <- str_c(str1, v[length(v)], sep = ", and ")
}
vec_6 <- c("s","o","s")
(vector_to_string(vec_6))
```

## 14.3.1.1 Exercises
###1. Explain why each of these strings don't match a \: "\","\\","\\\"?
```{r}

```

###2. How would you match the sequence "'\?
```{r}

```

##3. What patterns will the regular expression \..\..\.. match? How to represent it as a string?
```{r}

```


##14.3.2.1 Exercises
### 1. How would you match the literal string "$^$"?
```{r}


```

### 2. Given the corpus of common words in stringr::words, create regular expressions that find all words that: 
        1. Start with "y"
        2. End with "x"
        3. Are exactly three letters long.
        4. Have seven letters or more.
        
```{r}

```

## 14.3.3.1 Exercises
### 1. Create regular expressions to find all words that:
        1. Start with a vowel.
        2. That only contains constants.
        3. End with ed, but not with eed.
        4. End with ing or ise.
```{r}

```

### 2. Empirically verify the rule "i before e except after c"?
```{r}


```

### 3. Is "q" always followed by a "u"?
```{r}

```

### 4. Write a regular expression that matches a word if its probably written in British English, not American English?
```{r}

```

### 5. Create a regular expression that will match telephone numbers as commonly written in your country?
```{r}

```

## 14.3.4.1 Exercises
### 1. Describe the equivalents of ?, +, * in {m,n} form.
```{r}

```
### 2. Describe in words what these regular expressions match: 
    1. ^.*$
    2. "\\{.+\\}"
    3. \d{4}-\d{2}-\d{2}
    4. "\\\\{4}"
```{r}

```

### 3. Create regular expressions to find all words that:
    1. Start with three consonants.
    2. Have three or more vowels in a row.
    3. Have two or more vowel-consonant pairs in a row.
```{r}

```

## 14.3.5.1 Exercises
### 1. Describe in words what these expressions will match:
    1. (.)\1\1
    2. "(.)(.)\\2\\1"
    3. (..)\1
    4. "(.).\\1.\\1"
    5. "(.)(.)(.).*\\3\\2\\1"
```{r}

```
### 2. Construct regular expressions to match words that:
    1. Start and end with the same character.
    2. Contain a repreated pair of letters.
    3. Contain one letter repeated in at least three places.
```{r}

```

## 14.4.2 Exercises
### 1. For each of the following challenges, solve it by using both a singular expression and a combination of multiple str_detect() calls.
    1. Find all words that start or end with x.
    2. Find all words that start with a vowel and end with a constant.
    3. Are there any words that contain at least one of each different vowel?
```{r}

```

### 2. What word has the highest number of vowels? What words has the highest proportion of vowels?
```{r}

```

## 14.4.3.1 Exercises
### 1. In the previous example, you might have noticed that the regular expression matched "flickered", which is not a colour. Modify the regex to fix the problem.
```{r}


```

### 2. From the Harvard sentences data, extract:
    1. The first word from each sentence.
    2. All words ending in ing.
    3. All plurals.
    
```{r}

```

## 14.4.4.1 Exercises
### 1. Find all words that come after a "number" like "one", "two", "three"etc. Pull out both the number and the word.
```{r}

```

### 2. Find all contractions, separate out the pieces before and after the apostrophe.
```{r}

```

## 14.4.5.1 Exercises
### 1. Replace all forward slashes in a string with backslashes.
```{r}

```

### 2. Implement a simple version of str_to_lower() using replace_all()
```{r}

```

### 3. Switch the first and last letters in words. Which of those strings are still words?
```{r}

```

## 14.4.6.1 Exercises
### 1. Split up a string like "apples, pears, and bananas" into individual components.
```{r}

```

### 2. Why is it better to split up by boundary("word") than " "?
```{r}

```

### 3. What does splitting with an empty string ("")do? 
```{r}

```


## 14.5.1 Exercises
### 1. How would you find all strings containing \ with regex() vs. with fixed()?
```{r}

```

### 2. What are the five most common words in sentences?
```{r}

```

## 14.7.1 Exercises
### 1. Find all stringi functions that:
        1. Count the number of words.
        2. Find duplicated strings.
        3. Generate random text.
```{r}

```

### 2. How do you control the language that stri_sort() using for sorting?
```{r}

```















